### 2017-03-08 Hhh/Hhh.tex
Fixing spacing in itemize env and really sorting the page numbering
Final bits before submission

\section{Datasets and \acl{MC} samples}
\label{sec:hhh_datasets}
The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 p-p 
running period of the LHC. 
Signal and background events were generated using several different \ac{MC} event generators. The \texttt{MadGraph}
\cite{madgraph} matrix element generator was used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ, \WZ and \WW
events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
were used for the \Wjets and \Zellell backgrounds. This increases the number of background events
in regions with multiple jets, which are important for this analysis due to the presence of b-jets in the final state. 
The samples binned in jet multiplicity are combined with the
inclusive samples such that the fraction of events with each jet multiplicity is preserved.

Single top samples were produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of \ggHtohhtobbtautau
were generated in steps of $10\,\GeV$ between \mH $= 260$ -- $350\,\GeV$ using \texttt{PYTHIA 6} \cite{pythia64}. The maximum
 mass is $350\,\GeV$ because for the interpretation of a resonance as a Higgs boson the decay \PHiggs $\rightarrow$ \ttbar
starts to dominate beyond this mass. In all of the samples
\texttt{TAUOLA} \cite{tauola} is used to decay the tau leptons, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
Minimum bias events generated using \texttt{PYTHIA 6} are added to all \ac{MC} samples to model additional
interactions. The \ac{MC} samples are then reweighted so that the pileup distribution matches the
pileup distribution in data. The detector response to the final simulated particles is modelled using a \texttt{GEANT4}-based \cite{Geant4} detector simulation.

To better model the \Ztautau background an embedding technique is used. In this method, 
\Zmm events are selected in data and the muons are replaced by simulated taus. \texttt{TAUOLA} is used
to decay the taus, with the final state particles passed through the detector simulation. %and tau polarisation effects are modelled using \texttt{TauSpinner} \cite{TauSpinner}. 
Tracks in the inner tracking system, hits in the muon systems and energy deposits in the calorimeters
due to the simulated taus are combined with the remains of the \Zmm event after the detector signals
of the two muons originiating from the \PZ boson have been removed. This technique is also applied to 
a simulated \ttbar sample to estimate the \ttbar contamination in the \Zmm embedded sample. %This contribution
%needs to be subtracted from the \Ztautau background estimated using the embedded \Zmm sample to
%avoid double counting with the \ttbar \ac{MC}.

\section{Event selection and categorisation}
\label{sec:hhh_selection}
This section gives an overview of the event selection; a detailed description of the physics
objecs used in this analysis is given in chapter \ref{chap:objects}.

@@

\subsection{Categorisation}
\label{sec:hhh_selection_categories}
In both channels a selection on the transverse mass, \mT, between the electron or muon
and missing transverse energy, defined as,
\begin{equation}\label{eqn:hhh_selection_mt}
m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})}\,,
\end{equation}
is applied.
In this eqation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the azimuthal
angle between this light lepton and the missing transverse energy. The \mT~distributions for the \etau
and \mutau channels, using the selections as
described in sections \ref{sec:hhh_selection_mutau} and \ref{sec:hhh_selection_etau},
are shown in figure \ref{fig:Hhh_selection_mt}.

@@

In signal events the di-tau pair and di-jet pair 
are the decay products of a $125\,\GeV$ Higgs boson, therefore their invariant
masses should be close to $125\,\GeV$. To reduce background contributions
from events where the di-tau or di-jet mass is not compatible with
$125\,\GeV$, requirements are made on the di-jet invariant mass, and the di-tau
invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
a likelihood-based estimate of the di-tau mass using the visible decay products
of the taus and the reconstructed \MET. The use of this algorithm greatly
improves the separation between $\PZ\rightarrow\Pgt\Pgt$ and $\PHiggs\rightarrow\Pgt\Pgt$ events, 
which is of great importance for the \ac{SM} $\PHiggs\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
By requiring $70 < m_{jj} < 150\,\GeV$ and $90 < m_{\Pgt\Pgt} < 150\,\GeV$ a 
large number of background events can be rejected, while retaining
most of the signal. This is illustrated in figure \ref{fig:Hhh_selection_masscuts} for 
the 2jet-2tag category.

@@

In a kinematic fit constraints are made on the event kinematics, in the
case of this analysis these constraints are
$m(\Pgt_{1},\Pgt_{2}) = m_{\PHiggslight} = 125\,\GeV$  and
$m(\Pbottom_{1},\Pbottom_{2}) = m_{\PHiggslight} = 125\,\GeV$.
The kinematic observables related to the hadronic taus and jets
are varied within their uncertainties to fulfill these 
constraints. A $\chi^2$ cost term is introduced for each
observable that is varied with respect to the measurement,
the aim of the fit is to minimise the sum of these $\chi^2$ terms.

@@

The fitting procedure additionally modifies the masses of the b-jets as 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_bjetmass}
m_{\Pbottom_{1,2}}^{\text{fit}} = m_{\Pbottom{1,2}}\frac{E_{\Pbottom{1,2}}^{\text{fit}}}{E_{\Pbottom{1,2}}}.
\end{equation}
The $\chi^2$ term for each b-jet is calculated as $\chi_{\Pbottom 1,2}^2 = \frac{E_{\Pbottom 1,2}^{\text{fit}}-E_{\Pbottom 1,2}^{\text{meas}}}{\sigma_{\Pbottom 1,2}}$.

@@

@@

The likelihood function for data, whether observed or pseudo-data, is constructed as 
\begin{equation} \label{eqn:hhh_likelihood}
\mathcal{L}(\text{data}|\mu, \theta) = \Sigma_i\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot p(\tilde{\theta}|\theta),
\end{equation}
where $\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given by
\begin{equation}\label{eqn:hhh_poisson}
\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta))) = \frac{(\mu\cdot s_i(\theta) + b_i(\theta))^{n_i})}{n_i!}e^{-(\mu\cdot s_i(\theta)+b_i(\theta))},
\end{equation}
with $n_i$ the number of 
data events in bin $i$.

The first term in equation \ref{eqn:hhh_likelihood} integrates over all bins of the $m_{\PHiggs}^{\text{kinfit}}$ distribution 
in all channels and categories. The parameter $s$ represents the number of expected signal events
in each bin, and $b$ the number of expected background events. These are functions of 
$\theta$, the full set of nuisance parameters. The signal strength
modifier $\mu$ can represent different quantities depending on the normalisation of the 
signal expectation. In the case of the \Htohhtobbtautau analysis the signal is normalised
to $1\,\picobarn$, so the signal strength modifier represents
the \xsbr of a possible signal.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_008-d.pdf}}
\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/hhh_limit_comparison.pdf}}
\caption[Expected and observed upper limits at the 95\% CL on 
\xsbr for the \Htohhtobbtautau process.]{Expected and observed upper limits at the 95\% \ac{CL} on \xsbr  
for the \mbox{\Htohhtobbtautau} process. In (a) the three final states of \etau, \mutau and \tautau are combined. The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$ 
probability intervals on the expected limit  \cite{CMS-HIG-14-034}.
(b) Shows the expected upper limits at the 95\% \ac{CL} on \xsbr for the \Htohhtobbtautau
process, separated by channel. The blue line shows the limit for the \tautau channel, the green line for the \mutau channel, the red line
for the \etau channel and the black line the limit for all three channels combined. Up to around \mH~$= 320\,\GeV$ the \mutau channel is the most
sensitive, with the \tautau channel being more sensitive at higher masses.}
\label{fig:hhh_results_modelindep}
\end{center}
\end{figure}

%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=0.7\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure-aux_033.pdf}
%\caption{Expected 95\% CL upper limits on cross-section times branching ratio for the \Htohhtobbtautau process.
%The blue line represents the limit for the \tautau channel, the green line for the \mutau channel and the
%red line for the \etau channel. The black line shows the limit for all three channels combined. We see that up to around
%$m_H = 320$ GeV the \mutau channel is the most sensitive, with the \tautau channel being more sensitive at higher masses. FIXME remake this plot!}
%\label{fig:hhh_results_modelindep_perchannel}
%\end{center}
%\end{figure}

@@

\subsubsection{Interpretation in a type-II 2HDM}
\label{sec:hhh_results_modeldep_2HDM}
As discussed in section \ref{sec:theory_2HDM}, a \ac{2HDM} has more
free parameters than a particular \ac{MSSM} benchmark scenario. To leave
just two free parameters, it is enough to fix the masses of the five Higgs bosons
and take the quartic couplings to be zero.
For the interpretation shown here the assumption that $m_{\PHiggsps}=m_{\PHiggs}=m_{\PHiggs^+}=300\,\GeV$ is made.
The couplings of the Higgs bosons to quarks and leptons, and of the heavy Higgs bosons to other
particles, are defined by $\alpha$ and $\beta$, as in table \ref{tab:hhh_2HDM_couplings}.

The interpretations are made in the \cosba-\tanb~plane. Figure \ref{fig:HhhandAZh2HDMOverlaid}
shows the observed and expected exclusion at the 95\% \ac{CL} for the \Htohh
and \AtoZh analyses, overlaid on the \xsbr.
The exclusion contours have some interesting features, most of which can be explained by the couplings
in table \ref{tab:hhh_2HDM_couplings}. When \cosba=0, in the alignment limit, the couplings
of all particles are exactly \ac{SM}-like. This is reflected in the \Htohh and \AtoZh branching ratios, 
\begin{table}[htp]
\begin{center}
\caption{Couplings in the type-II 2HDM.}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Decay} & \textbf{Coupling}\\
\midrule
$\PHiggslight \rightarrow$ up-type quarks & $\text{SM coupling} \times \frac{\cos{\alpha}}{\sin{\beta}}$ \\
$\PHiggslight \rightarrow$ down-type quarks, leptons & $\text{SM coupling} \times -\frac{\sin{\alpha}}{\cos{\beta}}$ \\
$\PHiggs \rightarrow \PHiggslight\PHiggslight$ & $\sim$ \cosba $\times$ terms containing masses,\\
 & mixing angles, quartic couplings \\
$\PHiggsps \rightarrow \PZ\PHiggslight$ & $\sim$ \cosba\\
\bottomrule
\end{tabular}
\label{tab:hhh_2HDM_couplings}
\end{center}
\end{table}
which both vanish as \cosba~approaches zero. This leads to the corridor of non-exclusion down the 
centre of the graphs in figure \ref{fig:HhhandAZh2HDMOverlaid}. Additionally,
as the coupling of the \PHiggslight to pairs of b-quarks or tau leptons is proportional 
to $\frac{\sin{\alpha}}{\cos{\beta}}$, the branching ratios of \Htohhtobbtautau
and \AtoZhtolltautau vanish when $\alpha = 0$, leading to the corridor of non-exclusion
at \cosba $ > 0$ and low \tanb~in the \AtoZh figure. A similar corridor is starting
to become visible in the \xsbr structure of the \Htohh interpretation, but
the analysis is not yet sensitive enough to actually observe it.
%Additional regions of non--exclusion at low \tanb and \cosba near -1 are visible in the \Htohh 
%interpretation, these are a result of the complex \Htohh branching ratio.

>>>>

\section{Datasets and \acl{MC} samples}
\label{sec:hhh_datasets}
The dataset used for this analysis corresponds to the full dataset collected by the CMS experiment during the 2012 p-p 
running period of the LHC. 
Signal and background events are generated using several different \ac{MC} event generators. The \texttt{MadGraph}
\cite{madgraph} matrix element generator is used to generate samples of \Wjets, \Zellell, \ttbar and \ZZ, \WZ and \WW
events. In addition to samples with a mixture of jet multiplicities (`inclusive' samples), samples binned in jet multiplicity
are used for the \Wjets and \Zellell backgrounds. This increases the number of background events
in regions with multiple jets, which are important for this analysis due to the presence of b-jets in the final state. 
The samples binned in jet multiplicity are combined with the
inclusive samples such that the fraction of events with each jet multiplicity is preserved.

Single top samples are produced with the \texttt{POWHEG} \cite{powheg1,powheg2} generator. Samples of \ggHtohhtobbtautau
are generated in steps of $10\,\GeV$ between \mH $= 260$ -- $350\,\GeV$ using \texttt{PYTHIA 6} \cite{pythia64}. The maximum
 mass is $350\,\GeV$ because for the interpretation of a resonance as a Higgs boson the decay \PHiggs $\rightarrow$ \ttbar
starts to dominate beyond this mass. In all of the samples
\texttt{TAUOLA} \cite{tauola} is used to decay the tau leptons, and parton showering and hadronisation are modelled using \texttt{PYTHIA 6} \cite{pythia64}.
Minimum bias events generated using \texttt{PYTHIA 6} are added to all \ac{MC} samples to model additional
interactions. The \ac{MC} samples are then reweighted so that the pileup distribution matches the
pileup distribution in data. The detector response to the final simulated particles is modelled using a \texttt{GEANT4}-based \cite{Geant4} detector simulation.

To better model the \Ztautau background an embedding technique is used. In this method, 
\Zmm events are selected in data and the muons are replaced by simulated taus. \texttt{TAUOLA} is used
to decay the taus, with the final state particles passed through the detector simulation. %and tau polarisation effects are modelled using \texttt{TauSpinner} \cite{TauSpinner}. 
Tracks in the inner tracking system, hits in the muon systems and energy deposits in the calorimeters
due to the simulated taus are combined with the remains of the \Zmm event after the detector signals
of the two muons originating from the \PZ boson have been removed. This technique is also applied to 
a simulated \ttbar sample to estimate the \ttbar contamination in the \Zmm embedded sample. %This contribution
%needs to be subtracted from the \Ztautau background estimated using the embedded \Zmm sample to
%avoid double counting with the \ttbar \ac{MC}.

\section{Event selection and categorisation}
\label{sec:hhh_selection}
This section gives an overview of the event selection; a detailed description of the physics
objects used in this analysis is given in chapter \ref{chap:objects}.

@@

\subsection{Categorisation}
\label{sec:hhh_selection_categories}
In both channels a selection on the transverse mass, \mT, between the electron or muon
and missing transverse energy, defined as,
\begin{equation}\label{eqn:hhh_selection_mt}
m_{\text{T}} = \sqrt{2p_{\text{T}}E_{\text{T}}^{\text{miss}}(1-\cos{\Delta\phi})}\,,
\end{equation}
is applied.
In this equation \pT~is the transverse momentum of the electron or muon, and $\Delta\phi$ the azimuthal
angle between this light lepton and the missing transverse energy. The \mT~distributions for the \etau
and \mutau channels, using the selections as
described in sections \ref{sec:hhh_selection_mutau} and \ref{sec:hhh_selection_etau},
are shown in figure \ref{fig:Hhh_selection_mt}.

@@

In signal events the di-tau pair and di-jet pair 
are the decay products of a $125\,\GeV$ Higgs boson, therefore their invariant
masses should be close to $125\,\GeV$. To reduce background contributions
from events where the di-tau or di-jet mass is not compatible with
$125\,\GeV$, requirements are made on $m_{jj}$, the di-jet invariant mass, and on $m_{\Pgt\Pgt}$, the di-tau
invariant mass as reconstructed using the \texttt{SVFit} algorithm \cite{HDiscoveryCMS,SVFit}. This algorithm provides
a likelihood-based estimate of the di-tau mass using the visible decay products
of the taus and the reconstructed \MET. The use of this algorithm greatly
improves the separation between $\PZ\rightarrow\Pgt\Pgt$ and $\PHiggs\rightarrow\Pgt\Pgt$ events, 
which is of great importance for the \ac{SM} $\PHiggs\rightarrow\Pgt\Pgt$ analysis \cite{HDiscoveryCMS}.
By requiring $70 < m_{jj} < 150\,\GeV$ and $90 < m_{\Pgt\Pgt} < 150\,\GeV$ a 
large number of background events can be rejected, while retaining
most of the signal. This is illustrated in figure \ref{fig:Hhh_selection_masscuts} for 
the 2jet-2tag category.

@@

In a kinematic fit constraints are made on the event kinematics, in the
case of this analysis these constraints are
$m(\Pgt_{1},\Pgt_{2}) = m_{\PHiggslight} = 125\,\GeV$  and
$m(\Pbottom_{1},\Pbottom_{2}) = m_{\PHiggslight} = 125\,\GeV$.
The kinematic observables related to the hadronic taus and jets
are varied within their uncertainties to fulfil these 
constraints. A $\chi^2$ cost term is introduced for each
observable that is varied with respect to the measurement,
the aim of the fit is to minimise the sum of these $\chi^2$ terms.

@@

The fitting procedure additionally modifies the masses of the b-jets as 
~\vspace{-0.5\baselineskip}
\begin{equation}\label{eqn:kinfit_bjetmass}
m_{\Pbottom_{1,2}}^{\text{fit}} = m_{\Pbottom{1,2}}\frac{E_{\Pbottom{1,2}}^{\text{fit}}}{E_{\Pbottom{1,2}}}.
\end{equation}
The $\chi^2$ term for each b-jet is calculated as $\chi_{\Pbottom 1,2}^2 = \frac{E_{\Pbottom 1,2}^{\text{fit}}-E_{\Pbottom 1,2}^{\text{meas}}}{\sigma_{\Pbottom 1,2}}$, where `meas' denotes the measured value and `fit' the value given by the fit.

@@

\setlength{\itemsep}{-0.5\baselineskip}

@@

The likelihood function for data, whether observed or pseudo-data, is constructed as 
\begin{equation} \label{eqn:hhh_likelihood}
\mathcal{L}(\text{data}|\mu, \theta) = \Pi_i\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta) + b_i(\theta)) )\cdot p(\tilde{\theta}|\theta),
\end{equation}
where $\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta)))$ is given by
\begin{equation}\label{eqn:hhh_poisson}
\text{Poisson}(n_{i}|(\mu\cdot s_i(\theta)+b_i(\theta))) = \frac{(\mu\cdot s_i(\theta) + b_i(\theta))^{n_i})}{n_i!}e^{-(\mu\cdot s_i(\theta)+b_i(\theta))},
\end{equation}
with $n_i$ the number of 
data events in bin $i$.

The first term in equation \ref{eqn:hhh_likelihood} runs over all bins of the $m_{\PHiggs}^{\text{kinfit}}$ distribution 
in all channels and categories. The parameter $s$ represents the number of expected signal events
in each bin, and $b$ the number of expected background events. These are functions of 
$\theta$, the full set of nuisance parameters. The signal strength
modifier $\mu$ can represent different quantities depending on the normalisation of the 
signal expectation. In the case of the \Htohhtobbtautau analysis the signal is normalised
to $1\,\picobarn$, so the signal strength modifier represents
the \xsbr of a possible signal.

@@

\begin{figure}[h!]
\begin{center}
\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure_008-d.pdf}}
\subfloat[]{\includegraphics[width=0.5\textwidth]{Hhh/Plots/hhh_limit_comparison.pdf}}
\caption[Expected and observed upper limits at the 95\% CL on 
\xsbr for the \Htohhtobbtautau process.]{Expected and observed upper limits at the 95\% \ac{CL} on \xsbr  
for the \mbox{\Htohhtobbtautau} process. In (a) the three final states of \etau, \mutau and \tautau are combined. The green and yellow bands indicate the $\pm 1 \sigma $ and $\pm 2\sigma$ 
probability intervals on the expected limit  \cite{CMS-HIG-14-034}.
(b) Shows the expected upper limits at the 95\% \ac{CL} on \xsbr for the \Htohhtobbtautau
process, separated by channel. The blue line shows the limit for the \tautau channel, the green line for the \mutau channel, the red line
for the \etau channel and the black line the limit for all three channels combined. Up to around \mH~$= 320\,\GeV$ the \mutau channel is the most
sensitive, with the \tautau channel being more sensitive at higher masses.}
\label{fig:hhh_results_modelindep}
\end{center}
\end{figure}
\clearpage
%\begin{figure}[h!]
%\begin{center}
%\includegraphics[width=0.7\textwidth]{Hhh/Plots/CMS-HIG-14-034_Figure-aux_033.pdf}
%\caption{Expected 95\% CL upper limits on cross-section times branching ratio for the \Htohhtobbtautau process.
%The blue line represents the limit for the \tautau channel, the green line for the \mutau channel and the
%red line for the \etau channel. The black line shows the limit for all three channels combined. We see that up to around
%$m_H = 320$ GeV the \mutau channel is the most sensitive, with the \tautau channel being more sensitive at higher masses. FIXME remake this plot!}
%\label{fig:hhh_results_modelindep_perchannel}
%\end{center}
%\end{figure}

@@

\subsubsection{Interpretation in a type-II 2HDM}
\label{sec:hhh_results_modeldep_2HDM}
As discussed in section \ref{sec:theory_2HDM}, a \ac{2HDM} has more
free parameters than a particular \ac{MSSM} benchmark scenario. To leave
just two free parameters, it is enough to fix the masses of the five Higgs bosons
and take the quartic couplings to be zero.
For the interpretation shown here the assumption that $m_{\PHiggsps}=m_{\PHiggs}=m_{\PHiggs^+}=300\,\GeV$ is made.
The couplings of the Higgs bosons to quarks and leptons, and of the heavy Higgs bosons to other
particles, are defined by $\alpha$ and $\beta$, as in table \ref{tab:hhh_2HDM_couplings}.
\begin{table}[htp]
\begin{center}
\caption{Couplings in the type-II 2HDM.}
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Decay} & \textbf{Coupling}\\
\midrule
$\PHiggslight \rightarrow$ up-type quarks & $\text{SM coupling} \times \frac{\cos{\alpha}}{\sin{\beta}}$ \\
$\PHiggslight \rightarrow$ down-type quarks, leptons & $\text{SM coupling} \times -\frac{\sin{\alpha}}{\cos{\beta}}$ \\
$\PHiggs \rightarrow \PHiggslight\PHiggslight$ & $\sim$ \cosba $\times$ terms containing masses,\\
 & mixing angles, quartic couplings \\
$\PHiggsps \rightarrow \PZ\PHiggslight$ & $\sim$ \cosba\\
\bottomrule
\end{tabular}
\label{tab:hhh_2HDM_couplings}
\end{center}
\end{table}

The interpretations are made in the \cosba-\tanb~plane. Figure \ref{fig:HhhandAZh2HDMOverlaid}
shows the observed and expected exclusion at the 95\% \ac{CL} for the \Htohh
and \AtoZh analyses, overlaid on the \xsbr.
The exclusion contours have some interesting features, most of which can be explained by the couplings
in table \ref{tab:hhh_2HDM_couplings}. When \cosba=0, in the alignment limit, the couplings
of all particles are exactly \ac{SM}-like. This is reflected in the \Htohh and \AtoZh branching ratios, 
which both vanish as \cosba~approaches zero. This leads to the corridor of non-exclusion down the 
centre of the graphs in figure \ref{fig:HhhandAZh2HDMOverlaid}. Additionally,
as the coupling of the \PHiggslight to pairs of b-quarks or tau leptons is proportional 
to $\frac{\sin{\alpha}}{\cos{\beta}}$, the branching ratios of \Htohhtobbtautau
and \AtoZhtolltautau vanish when $\alpha = 0$, leading to the corridor of non-exclusion
at \cosba $ > 0$ and low \tanb~in the \AtoZh figure. A similar corridor is starting
to become visible in the \xsbr structure of the \Htohh interpretation, but
the analysis is not yet sensitive enough to actually observe it.

%Additional regions of non--exclusion at low \tanb and \cosba near -1 are visible in the \Htohh 
%interpretation, these are a result of the complex \Htohh branching ratio.
